---
title: "USE R! HAVE FUN! _ Solutions to week 1 exercises"
output: html_document
---

Hey guys! Sorry about the lateness, because I get a serious stomachache so I cannot get down to work until this afternoon. I hope that you have already finished the exercise. And do feel free to argue with me.     

And game time now!  

Prepared by: Yuan Tian(2016-4-17)  

#Solutions to week 1 exercises   

1. Besides R, there are a lot of software tools used in data science. Can you list **2** other tools? What are their advantages and disadvantages? And in which industries are those tools often used?  
- SPSS   
Advantages: SPSS has a user friendly UI(User interface), and the outputs are usually good looking with even default options.  
Disadvantages: SPSS is not so compatible with office software. And typically a UI will reduce the reproducibility of your analysis.     
Mainly applied: Sociology, economy.  
- SAS  
Advantages: SAS has dozens of portable packages suitable for different functions. It is also capable for operations research questions.  
Disadvatages: The license for SAS is rather expensive.  
Mainly applied: Almost every area.  
- Minitab  
Advatages: Minitab has a user friendly UI, while capable for lots of questions in quality control.  
Disadvantages: The apperance of Minitab's outputs are usually not good-looking. And a UI will reduce the reproducibility of your analysis.  

2. Install R on your computer. [Download R](https://www.r-project.org/).   
Just do it!  

3. RStudio is a powerful and productive user interface for R. I highly recommend you to install RStudio. [Download RStudio](https://www.rstudio.com/products/rstudio/download/).  
Just do it!  

4. You can also download the R tutorials from [R-bloggers](http://www.r-bloggers.com/).  
Just do it!  

5. Please find out how many data types are legal in R. List all of them along with their features. **There are at least 10 of them.**  
- Logical
- Integer
- Doulbe
- Complex
- Character
- Matrix
- Factor
- List
- NA
- NaH
- Data.frame
6. Using your knowledge about data type, type the following code:
```{r data type}
  x <- c(2)
  y <- as.logical(x)
  z <- as.character(y)
  x
  y
  z
```
x = 2 because the code "c(2)" means creating a number 2, and the operator "<- " means assigning 2 to x.  
y = TRUE because we coerce 2 to a logical number, namely "True" or "False"  
z = "TRUE" because we coerce y to a character, which means we store the character "TRUE" in z.  
Then type the following code:
```{test}
  x <- 1:6
  class(x)
  dim(x) = c(3,2)
  class(x)
```
 Why is the class of x changed?   
 This is because we coerce a vector into a matrix by assigning its dimensions.  
7. Study the control structures of R (if else, for loops, while loops, repeat, next, break).  
---------------  
if(your condition)  
{  
your code  
}  
else  
{  
your code  
}  
---------------  
for(your condition)  
{  
your code  
}  
---------------
while(your condition)  
{  
your code  
}  
---------------  
continue  
* Stop the current loop, and excute the next loop.*  
---------------  
break  
* Stop the whole loop.*  

8. Using the knowledge you've learned, program a function that can do the division. Remember that the denominator cannot be zero. (I understand this is may be a bit tough, so fill your code in the following example).     
```{r}
division <- function(nominator, denominator){  
  if(denominator == 0)
  {
    return("The denominator cannot be zero")
  }  
  else
  {
      return(nominator/denominator)
    }
} 
```
To test your function, type in "division(2, 3)", "division(2, 0)". The results will be 0.6667 and "Denominator is zero".   
9. Use your **division** function to solve the following equations:   
- 10/2  
- 6/5  
- 9/0  
```{r}
  division(10,2)
  division(6,5)
  division(9,0)
```
  
10. Program a function called **innerproduct**, whose purpose is to calculate the inner product of two vectors. To practice the use of **for** loops, try both multiplication and summation operations. **Do make sure the two vectors are of the same length.** Test your function.      
Tips: you can generate a vector in R by typing the following:   
```{test}
  x <- c(1, 2, 3, 4, 5)   
```   
```{r innerproduct}
  innerproduct <- function(a,b){
    if(length(a)!= length(b))
    return("The two vectors are not of the same length")
    else
    {sum = 0
      for(i in 1:length(a)){
        sum = sum + a[i]*b[i]
        i = i + 1}
    }
    return(sum)
  } 
  x <- c(1, 2 ,3)
  y <- c(3, 2, 1)
  z <- c(1, 2, 3, 4)
  innerproduct(x, y)
  innerproduct(x, z)
```